An improved metric for the analysis of swarms

### 2017-03-24 paper.tex
Restructure and updates

\section{Inter-agent vector magnitude effect on internal movement}\label{Section:StabilityMagnitude}
Figure \ref{methods:Stability5} shows the cohesion and repulsion vector contributions to $v_c(b)$ and $v_r(b)$ due to neighbour $b'$, as given in (\ref{eq:FlyToCentre1}, \ref{eq:Repulsion1}). Notice that the vectors are along the line of separation $bb'$. \\

@@

\begin{equation}\label{eq:FlyToCentre1}
v_{c}(b) = \frac{\mathlarger{\sum_{b' \in nbr(b)}}{bb'}}{|nbr(b)|}
\end{equation}‎

@@

\begin{equation}
\label{eq:Repulsion1}
v_{r}(b) =‎ -
\frac{1}{|R(b)|}
\left(
\mathlarger{\mathlarger{\sum_{b' \in rep(b)}}}
{\left( 1-\frac{|bb'|}{R_b} \right)}
{bb'}
\right)
\end{equation}‎

@@

Figure~\ref{methods:Stability1} shows two agents within each other's cohesion fields but sufficiently distant to be outside of the repulsion fields. In this case $|k_cv_c| > 0$ and $|k_rv_r| = 0$: the result is the agent's resultant magnitudes cause the agents to move towards each other. Table~\ref{tab:SampleReplusion0} shows the repulsion magnitude with a value of 0. The only influence on the agent pairs are cohesive vectors.

@@

\section{Internal movement and the null vector}\label{metric:StabilityNullVector}
When the two vectors (cohesion and repulsion) have magnitudes that are equal and opposite they produce a null vector. This indicates that two agents are optimally spaced for a given set of conditions. Although the agents are at an optimum position it does not mean the swarm is optimally distributed. If a swarm is in a confined space it is possible for an optimum position to be created where the vector magnitude is positive and there is a compression effect. This phenomenon is used in the identification of the emergent behaviour of \textit{area flooding}.

@@

\section{Residual internal movement (Jitter)}\label{metric:Jitter}
Due to the dynamic nature of a swarm maintaining optimum internal movement as in~(Figure \ref{methods:StabilityNullVector}) a stationary swarm is highly unlikely. The agent pairs will fluctuate between the 3 states~(Figures~\ref{methods:Stability2}, \ref{methods:Stability3} and \ref{methods:Stability4}). This alternation between the states is \textit{jitter}. The degree to which this variation occurs can be measured using either the change in distance between the agent pairs, or the change in the resultant magnitude between the agent pairs. Jitter is motion that is produced to maintain the structure of a swarm. A coordination algorithm that produces minimal jitter is generally more desirable. Jitter (the fluctuation in and between the states) is an indication of the efficiency of an algorithm and an integral component of a swarms measurable behaviour.

@@

\section{Distance metric}
The distance based internal movement is measured by identifying the mean length of the vectors between an agent and its neighbours. As with the \textit{agent resultant magnitude} a coordination algorithm produces `jitter' which is the variations from the mean. In the case of the distance based metric the jitter is identified by the changes in the distances rather than the changes in vector magnitude (\textit{agent resultant magnitude}). The distance metric is the mean and the standard deviation `jitter' of the inter-agent distances.

@@

\begin{equation}
\label{eq:SwarmStabilityDistance1}
\mu_d(b) = \frac{\mathlarger{\sum_{b' \in nbr(b)}}|bb'|}{\mathlarger{|nbr(b)|}}
\end{equation}

>>>>

\section{Inter-agent vector magnitude effect on internal movement}\label{Section:StabilityMagnitude}
Figure \ref{methods:Stability5} shows the cohesion and repulsion vector contributions to $v_c(b)$ and $v_r(b)$ due to neighbour $b'$, as given in (Equations \ref{eq:FlyToCentre1} and \ref{eq:Repulsion1}). Notice that the vectors are along the line of separation $bb'$. \\

@@

\begin{equation}\label{eq:FlyToCentre1}
v_{c}(b) = \frac{1}{|nbr(b)|}\left({\mathlarger{\sum_{b' \in nbr(b)}}{bb'}}\right)
\end{equation}‎

@@

\begin{equation}
\label{eq:Repulsion1}
v_{r}(b) =‎ -
\frac{1}{|rep(b)|}
\left(
\mathlarger{\mathlarger{\sum_{b' \in rep(b)}}}
{\left( 1-\frac{|bb'|}{R_b} \right)}
{bb'}
\right)
\end{equation}‎

@@

Figure~\ref{methods:Stability1} shows two agents within each other's cohesion fields but sufficiently distant to be outside of the repulsion fields. In this case $|k_cv_c| > 0$ and $|k_rv_r| = 0$: the result is the agent's resultant magnitude $v(b$  cause the agent to move towards is neighbour $b'$. Likewise the neighbours resultant magnitude $v(b')$ will cause the agent to move towards $b$. Table~\ref{tab:SampleReplusion0} shows the repulsion magnitude with a value of 0. The only influence on the agent pairs are cohesive vectors.

@@

\section{Internal movement and the null vector}\label{metric:StabilityNullVector}
When the two vectors (cohesion and repulsion) have magnitudes that are equal and opposite they produce a null vector. This indicates that two agents are optimally spaced for a given set of conditions. Although the agents are at an optimum position it does not mean the swarm is optimally distributed. If a swarm is in a confined space it is possible for an optimum position to be created where the vector magnitude is affected by a compression effect. This phenomenon is used in the identification of the emergent behaviour of \textit{area flooding}.

@@

\section{Residual internal movement (Jitter)}\label{metric:Jitter}
Due to the dynamic nature of a swarm, maintaining optimum internal movement as in~Figure \ref{methods:StabilityNullVector} is highly unlikely. The agent pairs will fluctuate between the 4 states~(Figures~\ref{methods:Stability1}, \ref{methods:Stability2}, \ref{methods:Stability3} and \ref{methods:Stability4}). This alternation between the states is \textit{jitter}. The degree to which this variation occurs can be measured using either the change in distance between the agent pairs, or the change in the resultant magnitude between the agent pairs. Jitter is motion that is produced to maintain the structure of a swarm. A coordination algorithm that produces minimal jitter is generally more desirable. Jitter (the fluctuation in and between the states) is an indication of the efficiency of an algorithm and an integral component of a swarms measurable behaviour.

@@

\section{Distance metric internal movement}
The distance based internal movement is measured by identifying the mean length of the vectors between an agent and its neighbours. As with the \textit{agent resultant magnitude} a coordination algorithm produces `jitter' which is the variations from the mean. In the case of the distance based metric the jitter is identified by the changes in the distances rather than the changes in vector magnitude (\textit{agent resultant magnitude}). The distance metric is the mean and the standard deviation `jitter' of the inter-agent distances.

@@

\begin{equation}
\label{eq:SwarmStabilityDistance1}
\mu_d(b) = \frac{1}{\mathlarger{|nbr(b)|}}\left({\mathlarger{\sum_{b' \in nbr(b)}}|bb'|}\right)
\end{equation}
